---
title: "math4753zeml24"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{math4753zeml24}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753ZEML24)
```

# Available Functions
## customplot.R
The function, customplot, plots a linear piece-wise regression. It takes in a variety of parameters, namely: the x value to split the regression (xk), the data frame to plot (dataframe), the name of the x variable (xvar), and the name of the y variable (yvar). An example of it running can be seen below
```{r}
MATH4753ZEML24::customplot(12, MATH4753ZEML24::fire, "DISTANCE", "DAMAGE")
```

## myboot2.R
The function, myboot2, plots a histogram of the function with the confidence interval. It takes in a variety of parameters, namely: the number of iterations to do (iter), the distribution to calculate (x), the function to apply to the distribution (fun), the confidence interval of the function (alpha), the numeric value of the plot symbol (cx), and any additional parameters. An example of it running can be seen below
```{r}
empty <- MATH4753ZEML24::myboot2(iter = 1000, x = rnorm(100, 0, 1), fun = mean, alpha = 0.95, cx = 1)
```

## mycltb.R
The function, mycltb, plots the histogram of the sample mean of a binomial distribution. It takes in a variety of parameters, namely: the sample size (n), the number of iterators (iter), the probability of success (p), and any additional parameters. An example of it running can be seen below
```{r}
MATH4753ZEML24::mycltb(n = 100, iter = 1000, p = 0.95)
```

## myncurve.R
The function, myncurve, creates a normal curve with a probability region. It takes in a variety of parameters, namely: the mean for the distribution (mu), the standard deviation for the distribution (sigma), and the number to calculate probability using (a). It returns a list containing the mean, standard deviation, and the area under the curve. An example of it running can be seen below
```{r}
MATH4753ZEML24::myncurve(mu = 0, sigma = 1, a = 1)
```

## ntickets.R
The function, ntickets, calculates the number of tickets given the overbooking problem within the acceptable range. It takes in a variety of parameters, namely: the number of tickets sold (N), the acceptable range of overbooking (gamma), and the probability of a ticket holder showing up (p). It returns a list containing the number of tickets for the discrete and continuous cases, the number of tickets sold, the probability of a ticket holder showing up, and the acceptable range of overbooking. An example of it running can be seen below
```{r}
MATH4753ZEML24::ntickets(N = 200, gamma = 0.05, p = 0.95)
```

## plotsamples.R
The function, plotsamples, plots a given number of iterations that have a size of choose(n). It takes in a variety of parameters, namely: the number of samples (n), the number of iterations (iter), and the time to wait (time). An example of it running can be seen below
```{r}
MATH4753ZEML24::plotsamples(n = 10, iter = 10)
```

# Available Data
## FIRE Dataset
The FIRE dataset is a dataset with 15 measurements and 2 columns. The first column is the cost of the fire, and the second column is the distance to the nearest fire station. In short, this dataset is a collection of fires and the distances from those fires to the nearest fire station.
```{r}
head(MATH4753ZEML24::fire)
```

